Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-20 paper/paper.qmd
Update clean_data script
Deleted some unnecessary files

```{r}
data <- read.csv("../data/01-raw_data/president_polls.csv")
skim(data)

@@

pollster

pollscore, numeric_grade

sponsor_candidate, sponsor_candidate_party

sample_size

```{r mutate days_towards_election}
data_a <- data %>% 
  select(end_date) %>% 
  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))

# Define the election date
election_date <- as.Date("11/5/24", format="%m/%d/%y")

# Calculate the days towards the election date
data_a <- data_a %>% 
  mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))

data$days_towards_election = data_a$days_towards_election
```

@@

```{r}
selected_columns <- c(
  "pollster", 
  "sponsors", 
  "numeric_grade", 
  "pollscore", 
  "methodology", 
  "transparency_score", 
  "state", 
  "start_date", 
  "end_date", 
  "sponsor_candidate", 
  "sponsor_candidate_party", 
  "question_id", 
  "sample_size", 
  "population", 
  "population_full",
  "tracking", 
  "notes", 
  "source", 
  "internal", 
  "partisan", 
  "race_id", 
  "ranked_choice_reallocated", 
  "ranked_choice_round", 
  "hypothetical", 
  "party", 
  "answer", 
  "candidate_name", 
  "pct"
)
data %>% 
  select(all_of(selected_columns))
```

>>>>

```{r}
data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
skim(data)

@@

@@
